Towards a self healing swarm through the removal of voids and anomalies

### 2018-07-15 paper.tex
Graphs Fix

Equation~\eqref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent's neighbour's make with the first detected neighbour.
%% 
%% \begin{center}
%% \begin{equation}‎
%% \label{eq:ConcaveVoidPhysics2}
%% G_b \buildrel \Delta \over =‎ gap(S_b,\angle<180^\circ)
%% \end{equation}‎
%% \end{center}

Figure~\ref{algo:getNeighbourAngles} shows the logic to produce the sorted neighbour/angle dictionary. $sort(.)$ sorts the dictionary set generated in~\eqref{eq:ConcaveVoidPhysics1} by ascending angle to produce a dictionary of neighbour agents with their relative angle to the first detected neighbour as shown in~Fig.~\ref{reduced:Perimeter1}.

@@

As all the agents have the same field effects the `visibility' of two neighbours can be determined. The angle and distance of each neighbour pair allows the cosine rule to be used to calculate the distance the neighbours are apart as shown in~\eqref{eq:CosineRule1} and Fig.~\ref{reduced:Triangulate}. The distance is checked against the neighbour range, if the distance is $\leq N_b$ where $N_b$ is the \textit{neighbour field} then it can be assumed that the neighbours have `sight' of each other.

@@

The full visibility check~(Fig.~\ref{algo:CheckVisibility}) takes each pair in turn and using the cosine rule~\eqref{eq:CosineRule1} checks for a `visibility gap'.

@@

\section{Concave reduction mathematical model}\label{concave:ConcaveVoidReduction1}
As part of identifying a perimter agents a set of agents sorted by angle and a set ($b.gap \equiv G_b$) consisting of the first two agents identified as creating a `gap' in agent $b$'s neighbours. Equation~\eqref{eq:ConcaveVoidPhysics3} calculates the centroid of the gap agents.

Equation~\eqref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent's neighbour's make with the first detected neighbour. $nbr(b)$ returns a set of all an agents neighbours.

@@

$D(b)$~is a vector derived from the identified centroid of the neighbour gap~($G_b$) to the parent agent~($b$). This new vector is the \textit{concave vector} used to implement the concave reduction movement~\eqref{eq:ConcaveVoidPhysics3a}.

@@

This derived movement is specifically for reducing the anomaly of which the agent is a part. The concave reduction movement needs to be enhanced to take into consideration an agent's surroundings. Due to proximity it can be assumed that there are no agents in the path between the agent and the gap, however there may be an obstacle. The \textit{concave vector} must include an obstacle avoidance component~$v_o(b)$. As with all the previous vector based calculations a weighting is applied to the calculated \textit{concave vector}~$k_{cr}$ to allow the model to vary the intensity of the effect. The resultant vector is then normalised to produce the \textit{concave reduction vector} as shown in~\eqref{eq:ConcaveVoidPhysics4}. 
%
\begin{equation}
\label{eq:ConcaveVoidPhysics4}
V(b) = (k_{cr}D(b) + k_ov_o(b))\string^
\end{equation}
%
\section{Effect of concave reduction on swarm structure}
If there is a `gap' on a perimeter then the \textit{concave reduction vector} is applied instead of the normal \textit{interaction vector}. To test this effect a baseline is established for a comparison.

>>>>

Equation~\ref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent's neighbour's make with the first detected neighbour.
%% 
%% \begin{center}
%% \begin{equation}‎
%% \label{eq:ConcaveVoidPhysics2}
%% G_b \buildrel \Delta \over =‎ gap(S_b,\angle<180^\circ)
%% \end{equation}‎
%% \end{center}

Figure~\ref{algo:getNeighbourAngles} shows the logic to produce the sorted neighbour/angle dictionary. $sort(.)$ sorts the dictionary set generated in~\ref{eq:ConcaveVoidPhysics1} by ascending angle to produce a dictionary of neighbour agents with their relative angle to the first detected neighbour as shown in~Fig.~\ref{reduced:Perimeter1}.

@@

As all the agents have the same field effects the `visibility' of two neighbours can be determined. The angle and distance of each neighbour pair allows the cosine rule to be used to calculate the distance the neighbours are apart as shown in~\ref{eq:CosineRule1} and Fig.~\ref{reduced:Triangulate}. The distance is checked against the neighbour range, if the distance is $\leq N_b$ where $N_b$ is the \textit{neighbour field} then it can be assumed that the neighbours have `sight' of each other.

@@

The full visibility check~(Fig.~\ref{algo:CheckVisibility}) takes each pair in turn and using the cosine rule~\ref{eq:CosineRule1} checks for a `visibility gap'.

@@

\section{Concave reduction mathematical model}\label{concave:ConcaveVoidReduction1}
As part of identifying a perimter agents a set of agents sorted by angle and a set ($b.gap \equiv G_b$) consisting of the first two agents identified as creating a `gap' in agent $b$'s neighbours. Equation~\ref{eq:ConcaveVoidPhysics3} calculates the centroid of the gap agents.

Equation~\ref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent's neighbour's make with the first detected neighbour. $nbr(b)$ returns a set of all an agents neighbours.

@@

$D(b)$~is a vector derived from the identified centroid of the neighbour gap~($G_b$) to the parent agent~($b$). This new vector is the \textit{concave vector} used to implement the concave reduction movement~\ref{eq:ConcaveVoidPhysics3a}.

@@

This derived movement is specifically for reducing the anomaly of which the agent is a part. The concave reduction movement needs to be enhanced to take into consideration an agent's surroundings. Due to proximity it can be assumed that there are no agents in the path between the agent and the gap, however there may be an obstacle. The \textit{concave vector} must include an obstacle avoidance component~$v_o(b)$. As with all the previous vector based calculations a weighting is applied to the calculated \textit{concave vector}~$k_{cr}$ to allow the model to vary the intensity of the effect. The resultant vector is then normalised to produce the \textit{concave reduction vector} as shown in~\ref{eq:ConcaveVoidPhysics4}. 
%
\begin{equation}
\label{eq:ConcaveVoidPhysics4}
V(b) = (k_{cr}D(b) + k_ov_o(b))\string^
\end{equation}
%
\section{Effect of concave reduction on swarm structure}
If there is a `gap' on a perimeter then the \textit{concave reduction vector} is applied instead of the normal \textit{interaction vector}. To test this effect a baseline is established for a comparison.
